An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-23 neurips-19/poly-embed.tex
Fleshed out invariance in ones direction with simpler version
Minor changes in top k appendix

We next show that $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$. \begin{lemma}\label{lem:top-k-optimal-corners}
  For all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
\end{lemma}
\begin{proof}
  Let us first simplify $L'$:
  \[
    L'(u)_y = \left( 1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+~.
  \]
  Next, we observe that $L'$ is invariant in the $\ones$ direction, so without loss of generality, we can restrict our consideration to reports so that $u_{[n]} = 0$.
  To see this,
  \begin{align*}
  L'(u + \alpha \ones)_y &=\left(\frac{1}{k} \sum_{i=1}^k ((u+\alpha \ones) + \ones - e_y)_{[i]} - (u_y + \alpha) \right)_+\\
  &= \left(\frac{1}{k} \left[k\alpha + \sum_{i=1}^k (u + \ones - e_y)_{[i]}\right] - (u_y + \alpha) \right)_+\\
  &= \left(\alpha + \frac{1}{k} \left[\sum_{i=1}^k (u + \ones - e_y)_{[i]}\right] - (u_y + \alpha) \right)_+\\
  &= \left(\frac{1}{k} \left[\sum_{i=1}^k (u + \ones - e_y)_{[i]}\right] - u_y \right)_+\\
  &= L(u)_y
  \end{align*}

  We first claim that for all $y \in \Y$, the minimum of $L(u)_y$ is achieved by some $u \in [0,1]^n$.
  Observe that if $u_{[1]} > 1$, the value of the loss gets ``cropped'' and will be the same by reporting $u_{[1]} = u_{[n]} + 1 = 1$. \jessiet{Flesh this out later.}
  Since $u_{[n]} = 0 \implies u_{[1]} \in [0,1]$, we can then observe there is some $u \in \prop{L'}$ so that $u \in [0,1]^n$.

>>>>

We next show that $\U = \{u \in \{0,1\}^n : \|u\|_0 \leq k\}$ is always represented among the optimizers of $L'$. \begin{lemma}\label{lem:top-k-optimal-corners}
  For all $p \in \simplex$ we have $\prop{L'}(p) \cap \U \neq \emptyset$.
\end{lemma}
\begin{proof}
  Let us first simplify $L'$:
  \[
    L'(u)_y = \left( 1 - u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \right)_+~.
  \]
  Next, we observe that $L'$ is invariant in the $\ones$ direction, so without loss of generality, we can restrict our consideration to reports so that $u_{[n]} = 0$.
  To see this,
  \begin{align*}
    L'(u + \alpha \ones)_y &= \left( 1 - (u_y + \alpha) + \frac{1}{k} \sum_{i=1}^k ((u + \alpha) - e_y)_{[i]} \right)_+\\
    &= \left( 1 - (u_y + \alpha) + \frac{1}{k}\left[ \alpha k + \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
    &= \left( 1 -u_y - \alpha + \alpha + \frac{1}{k}\left[ \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
    &= \left( 1 -u_y + \frac{1}{k}\left[ \sum_{i=1}^k (u - e_y)_{[i]} \right] \right)_+\\
  &= L'(u)_y
  \end{align*}

  We first claim that for all $y \in \Y$, the minimum of $L(u)_y$ is achieved by some $u \in [0,1]^n$.
  Observe that if $u_{[1]} > 1$, the value of the loss gets ``cropped'' and will be the same by reporting $u_{[1]} = u_{[n]} + 1 = 1$. \jessiet{Flesh this out later.}
  Since $u_{[n]} = 0 \implies u_{[1]} \in [0,1]$, we can then observe for all $p \in \simplex$, there is some $u \in \prop{L'}(p)$ so that $u \in [0,1]^n$.
